Supplemental material for:

### 2022-02-09 analysis/supplementary-materials/supplemental.Rmd
Fix Fig S1. Requires manual editing now, boo.

regionsample <- filter(bw_400hz, region_id == 6)
peaksample <- filter(peak_tbl, between(dt, 
                                       first(regionsample$dt), 
                                       last(regionsample$dt))) %>% 
  arrange(dt) %>% 
  mutate(peak_lbl = seq(n()))

@@

pA <- ggplot(regionsample, aes(dt, jerk_smooth)) +
  geom_line() +
  geom_point(aes(y = height, color = is_beat), data = peaksample) +
  geom_text(aes(y = height, label = peak_lbl), 
            data = peaksample, 
            vjust = -0.3) +
  scale_color_manual(values = c("red", "blue")) +
  labs(x = "", y = "Y") +
  theme_classic(base_size = 10) +
  theme(axis.title.x = element_blank(),
        legend.position = "FALSE")

@@

cowplot::plot_grid(pA, pB, pC, pD, ncol = 2, labels = "AUTO")
```

>>>>

regionsample <- filter(bw_400hz, region_id == 6) %>% 
  mutate(secs = as.numeric(dt - min(dt), unit = "secs"))
peaksample <- filter(peak_tbl, between(dt, 
                                       first(regionsample$dt), 
                                       last(regionsample$dt))) %>% 
  arrange(dt) %>% 
  mutate(peak_lbl = seq(n()),
         secs = as.numeric(dt - min(regionsample$dt)))

@@

pA <- ggplot(regionsample, aes(secs, jerk_smooth)) +
  geom_line() +
  geom_point(aes(y = height, color = is_beat), data = peaksample) +
  geom_text(aes(y = height, label = peak_lbl), 
            data = peaksample, 
            vjust = -0.3) +
  scale_color_manual(values = c("red", "blue")) +
  labs(x = "Seconds", y = "Y") +
  theme_classic(base_size = 10) +
  theme(legend.position = "FALSE")

@@

# Figure S1 requires manual adjustments. Save to .svg, edit in Inkscape, then
# export back to PNG and insert here.
S1 <- cowplot::plot_grid(pA, pB, pC, pD, ncol = 2, labels = "AUTO")
ggsave(here::here("analysis/figures/S1.svg"), S1)
cowplot::ggdraw() +
  cowplot::draw_image(here::here("analysis/figures/S1_edited.svg"))
```
